\cleardoublepage 

# (APPENDIX) Appendix {-}

# Data Dictionary

In order to more easily explore and line up the data, the dictionary below was constructed. Note, that feature names that appear in parenthesis were the original names of the columns, and were renamed to more easily understand the features. 

<style>
table {
font-size: 10px;
}
</style>

#### Identifiers {-}

```{r, echo=FALSE}
htmltools::includeHTML("data/data_dictionary/Identifier.html")
```

#### Demographics {-}

```{r, echo=FALSE}
htmltools::includeHTML("data/data_dictionary/Demographic.html")
```

#### Devices {-}

```{r, echo=FALSE}
htmltools::includeHTML("data/data_dictionary/Devices.html")
```

#### Internet {-}

```{r, echo=FALSE}
htmltools::includeHTML("data/data_dictionary/Internet.html")
```

#### Social Media {-}

```{r, echo=FALSE}
htmltools::includeHTML("data/data_dictionary/Social Media.html")
```

#### Dependencies {-}

```{r, echo=FALSE}
htmltools::includeHTML("data/data_dictionary/Dependency.html")
```

#### Society {-}

```{r, echo=FALSE}
htmltools::includeHTML("data/data_dictionary/Society.html")
```

#### Books {-}

```{r, echo=FALSE}
htmltools::includeHTML("data/data_dictionary/Books.html")
```

#### Other {-}

```{r, echo=FALSE}
htmltools::includeHTML("data/data_dictionary/Other.html")
```