--- 
title: "EDAV Final 2019"
author: "Woo Jin Kim, Matt Mackenzie, Mamunur Rashid"
date: "`r Sys.Date()`"
description: "[Book description]"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
colorlinks: yes
github-repo: mbmackenzie/edav-f19-final
---

# Introduction {-}

Introduction

## Data Dictionary {-}

In order to more easily explore and line up the data, the dictionary below was constructed. Note, that feature names that appear in parenthesis were the original names of the columns, and were renamed to more easily understand the features. 

<style>
table {
font-size: 10px;
}
</style>

### Identifiers {-}

```{r, echo=FALSE}
htmltools::includeHTML("data/data_dictionary/Identifier.html")
```

### Demographics {-}

```{r, echo=FALSE}
htmltools::includeHTML("data/data_dictionary/Demographic.html")
```

### Devices {-}

```{r, echo=FALSE}
htmltools::includeHTML("data/data_dictionary/Devices.html")
```

### Social Media {-}

```{r, echo=FALSE}
htmltools::includeHTML("data/data_dictionary/Social Media.html")
```

### Dependencies {-}

```{r, echo=FALSE}
htmltools::includeHTML("data/data_dictionary/Dependency.html")
```

### Society {-}

```{r, echo=FALSE}
htmltools::includeHTML("data/data_dictionary/Society.html")
```

### Books {-}

```{r, echo=FALSE}
htmltools::includeHTML("data/data_dictionary/Books.html")
```

### Other {-}

```{r, echo=FALSE}
htmltools::includeHTML("data/data_dictionary/Other.html")
```